Anxiety_vis

### 2023-04-20 Anxiety_Vis.Rmd
Finalized code for final presentation.

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUXOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
```

@@

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = .01, label = "Q1") +
  annotate("text", x = 8, y = .01, label = "Mean") +
  annotate("text", x = 13, y = .01, label = "Q3")

@@

ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  labs(subtitle = "Broken up by Discharge Date")+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 49, label = "Q1") +
  annotate("text", x = 8, y = 49, label = "Mean") +
  annotate("text", x = 13, y = 49, label = "Q3") 
```

@@

#### Race
```{r}
#Overall race
Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
   geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

Example of plot for 1-5 days discharge
```{r}
#Create a New Data Set with an Average Anxiety Variable and Race
Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 6-10 days
RaceDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 11-15 days
RaceDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 16+ days
RaceDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

## GENDER IDENTITY
Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Anxiety Variable and Gender
Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUXOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 59, label = "Q1") +
  annotate("text", x = 8, y = 59, label = "Mean") +
  annotate("text", x = 13, y = 59, label = "Q3") 
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUXOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Anxiety Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
GenderDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
GenderDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
GenderDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
GenderDF4<-GenderDF4[1:120,]

@@

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Anxiety Variable and Track
Mothership_Mean_CUXOS_Track<-Mothership_Long %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 45, label = "Q1") +
  annotate("text", x = 8, y = 45, label = "Mean") +
  annotate("text", x = 13, y = 45, label = "Q3") 
```

Break it up by duration group (Treatment track)
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
TrackDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
TrackDF1<-TrackDF1[1:20,]

@@

##### 5-10 Days
TrackDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
TrackDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
TrackDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
TrackDF4<-TrackDF4[1:80,]

@@

```{r}
ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Anxiety Variable and Education
Mothership_Mean_CUXOS_Ed<-Mothership_Long %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 49, label = "Q1") +
  annotate("text", x = 8, y = 49, label = "Mean") +
  annotate("text", x = 13, y = 49, label = "Q3") 
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
EducationDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
EducationDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
EducationDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
EducationDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF4<-EducationDF4[1:180,]

# plot
Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
```
### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Anxiety Variable and Year
Mothership_Mean_CUXOS_Year<-Mothership_Long %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

>>>>

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUXOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

# Mothership_Mean_CUXOS20<-Mothership_Long20 %>%
#   group_by(TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  theme_classic()

@@

ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  labs(subtitle = "Broken up by Duration of Treatment")
  #  +
  # geom_vline(xintercept = 5,alpha =.25)+
  # geom_vline(xintercept = 8,alpha =.25)+
  # geom_vline(xintercept = 13,alpha =.25)+
  # annotate("text", x = 5, y = 49, label = "Q1") +
  # annotate("text", x = 8, y = 49, label = "Mean") +
  # annotate("text", x = 13, y = 49, label = "Q3") 
```

@@

#### Race
```{r}

Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      )

Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")

Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]

#Create a Time Variable
Mothership_Long_anx$TxDay <- NA
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10

#Overall race
Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS_Race<-Mothership_Mean_CUXOS_Race[1:70,]
Mothership_Mean_CUXOS_Race
# plot
ggplot(data=subset(Mothership_Mean_CUXOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,60,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Example of plot for 1-5 days discharge
```{r}
#Create a New Data Set with an Average Anxiety Variable and Race
Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 6-10 days
RaceDF2<-Mothership_Long_anx %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 11-15 days
RaceDF3<-Mothership_Long_anx %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

######## 16+ days
RaceDF4<-Mothership_Long_anx %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

## GENDER IDENTITY
Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Anxiety Variable and Gender

Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS_Gender <-filter(Mothership_Mean_CUXOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )

#Create the Anxiety Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUXOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUXOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Anxiety Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
GenderDF2<-Mothership_Long_anx %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
GenderDF3<-Mothership_Long_anx %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
GenderDF4<-Mothership_Long_anx %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
GenderDF4<-GenderDF4[1:120,]

@@

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Anxiety Variable and Track
Mothership_Mean_CUXOS_Track<-Mothership_Long_anx %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E","gold3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group (Treatment track)
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
TrackDF1<-Mothership_Long_anx %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
TrackDF1<-TrackDF1[1:20,]

@@

##### 5-10 Days
TrackDF2<-Mothership_Long_anx %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
TrackDF3<-Mothership_Long_anx %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
TrackDF4<-Mothership_Long_anx %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
TrackDF4<-TrackDF4[1:80,]

@@

```{r}
ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Anxiety Variable and Education
Mothership_Mean_CUXOS_Ed<-Mothership_Long_anx %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2",
                              "#798897","#FD85AE"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)

ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","lightgrey","lightgrey",
                              "gold3","lightgrey","lightgrey",
                              "lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)
```

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
EducationDF1<-Mothership_Long_anx %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 5-10 Days
EducationDF2<-Mothership_Long_anx %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 10-15 Days
EducationDF3<-Mothership_Long_anx %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

##### 16+ Days
EducationDF4<-Mothership_Long_anx %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF4<-EducationDF4[1:180,]

# plot
Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2",
                              "#798897","#FD85AE","firebrick4"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
```
### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Anxiety Variable and Year
Mothership_Mean_CUXOS_Year<-Mothership_Long_anx %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2",
                              "firebrick4","#FD85AE","#798897"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
